---
title: Working Paper Template
author: 
  - name: Dario Meili
    affiliation: Development Economics Group, ETH Zurich, Switzerland, <dario.meili@nadel.ethz.ch>
  - name: Second Author
    affiliation: Second istitution
date: \today
abstract: |
   You can include the text for your abstract here. 
thanks: |
  Thanks ...
keywords: [Keyword A, Keyword B, Keyword, C]
jel: [I24, I32, J15, J16]
bibliography: template-bib.bib
csl: 'apa-no-ampersand.csl'
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    template: template.tex
    extra_dependencies: ["flafter", "placeins"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,
                      warning=FALSE,
                      echo = FALSE, 
                      fig.path='figures/', 
                      floatfoot.envs = c("figure", "table", "longtabu")) 
```

```{r loadlibraries, include=FALSE}
library(tidyverse)
library(magrittr)
library(knitr)
library(kableExtra)
library(estimatr)
library(modelsummary)
library(gtsummary)
library(aswp)
```

```{r loaddata, include=FALSE}
# load custom functions
source("functions/functions.R")

# load data or run cleaningfile in case file does not exist
if (!file.exists("data/cleaned.Rda")) {
  source("code/cleaning.R")
}

# run external analyses
source("code/analysis.R")

ggplot2::theme_set(ggplot2::theme_bw())  ## (this just globally sets the ggplot2 theme to theme_bw)
```


# Introduction {#introduction}

I can cite @Illing2020 like this. I can also cite in parentheses [@Illing2020].

The remainder of this paper proceeds as follows. Section \@ref(background) introduces X. Section \@ref(methods) describes the empirical strategy to estimate Y. Section \@ref(data) presents more information on the data. Section \@ref(results) presents the results of the analysis. Section \@ref(conclusion) concludes.

The command `\FloatBarrier` makes sure that floats such as tables and figures stay in their section.
\FloatBarrier 

# Background {#background}

\FloatBarrier

# Methodology {#methods}

\FloatBarrier

# Data {#data}

In many empirical papers you will have a Table One, aka a table with sample statistics or a balance table in case of an experimental paper. The easiest way is to use `gtsummary::tbl_summary` to print a table with summary stats. 

```{r summary1}
mtcustom %>% 
  select(mpg:drat) %>% 
  tbl_summary() %>% 
  as_kable_extra(caption = "Summary statistics with gtsummary", 
                 booktabs = T)
```

At the moment the table caption appears below the table. I have not figured out yet why it does that.


We can also make a balance table. 

```{r balance, floatfoot = "(ref:note-balance)"}
datasummary_balance(~am, 
                    data = mtcustom, 
                    output = "kableExtra", 
                    title = "A balance table using modelsummary", 
                    notes = "We can either add notes as part of the modelsummary/datasummary function call")
                    
```

(ref:note-balance) **Notes:** Or as part of the floatfoot environment provided by the aswp package. 

We can also generate a balance table using the `gtsummary` package, just as before

```{r balance2}
mtcustom %>% 
  tbl_summary(by=am
              ) %>% 
  add_p() %>% 
  as_kable_extra(caption="Balance Table with gtsummary", 
                 booktabs=T) %>% 
  add_footnote(label = c("We can also add footnotes here"))
```


\FloatBarrier

# Results {#results}

When we plot results the `floatfoot` environment allows us to add long notes to figures.

(ref:note-figure) **Notes:** Place the figure notes here to make sure they appear below the figure. I'm writing a bit more to show how nicely it works even with longer figure notes. 

```{r figure, fig.cap="A Figure", floatfoot= "(ref:note-figure)"}
mtcustom %>% 
  group_by(cyl, am) %>% 
  summarize(mean_mpg = mean(mpg)) %>% 
  ggplot(aes(x=cyl, y=mean_mpg, fill=am)) +
  geom_col(position = "dodge") +
  scale_fill_viridis_d()
  
```


We can also use modelsummary for regression tables. 

```{r reg, floatfoot = "(ref:note-reg)"}
modelsummary(list(m1, m2), 
             output = "kableExtra", 
             stars = TRUE, 
             title = "Title for the table", 
             notes = list("\\emph{Notes:} I can add notes", "And even more notes if I want")
             )
```

(ref:note-reg) **Notes:** This is a table not that is not a part of the table, but rather attached to it below. This might be useful for some table-making functions that are not very flexible when it comes to table notes. 

\FloatBarrier

# Conclusion {#conclusion}

\clearpage

# References {.unnumbered}

::: {#refs}
:::

```{=tex}
\appendix
\clearpage
```
# Appendix Section 

\FloatBarrier
